---
title: "Homework 2"
author: "Varun Saxena"
format:
  pdf:
    output-file: "saxena-v-hwk2-1"
    output-ext:  "pdf"
    header-includes:
      - \usepackage{float}
      - \floatplacement{table}{H}
---

Repository: https://github.com/varunsaxena2/saxena-v-hwk2-2/tree/main

\noindent 1. Here is the line graph with the number of hospitals filing multiple reports per year
```{r}
#| echo: false

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, readr, readxl, hrbrthemes, fixest,
               scales, gganimate, gapminder, gifski, png, tufte, plotly, OECD,
               ggrepel, survey, foreign, devtools, pdftools, kableExtra, modelsummary,
               kableExtra)

library(knitr)
#library(ggbeeswarm)

load("Hwk2_workspace.Rdata")

ggplot(num_hospitals_multiple_reports, aes(x = year, y = num_hospitals)) +
  geom_line() + 
  labs(x = "Year", y = "Number of Hospitals", title = "Number of Hospitals with Multiple Reports")
```

\newpage
\noindent 2. The number of unique hospitals based on the hospital ID is `r distincthost`.

\newpage
\noindent 3. 

```{r}
#|echo: false
data %>% 
  ggplot(aes(x = year, y = tot_charges)) +
  geom_jitter(alpha = 0.2) +
  geom_violin(alpha = 0.1, draw_quantiles = c(0.1))


```

\newpage
\noindent 4. 

\newpage
\noindent 10. I had a difficult time reading in the data and getting it all to download, so I was only able to get through question 1. I also have no experience with R outside of Homework 1, so figuring out how the ggplots work in conjunction with Quarto is an ongoing learning process.
